### 2021-07-21 chapters/rq2/1_clustering_mutants.tex

\section{Implementation of subtractive clustering}
For the same reasons as in Chapter \ref{ch:fcm_implementation} we select a library that implements the subtractive clsutering algorithm.
The research paper of the mountain and subtractive algorithms are referenced in the survey paper of Du et al\cite{Du2010Clustering:Approach}.
Based on the paper of the theory of the subtractive algorithm\cite{Chiu1994FuzzyEstimation} we found an existing implementation\cite{matlabSubtractive}.
The implementation is professionally build and maintained by Matlab\cite{matlabSubtractive}.
Matlab is a tool commonly used in the academic world and is professionally maintained for this reason we decided to use their implementation of subtractive clustering.

>>>>

\section{Implementation of subtractive clustering}
For the same reasons as in Chapter \ref{ch:fcm_implementation} we select a library that implements the subtractive clustering algorithm.
The research paper of the mountain and subtractive algorithms are referenced in the survey paper of Du et al.\cite{Du2010Clustering:Approach}.
Based on the paper of the theory of the subtractive algorithm\cite{Chiu1994FuzzyEstimation} we found an existing implementation\cite{matlabSubtractive}.
The implementation is professionally build and maintained by Matlab\cite{matlabSubtractive}.
Matlab is a tool designed for the academic world and is professionally maintained for this reason we decided to use their implementation of subtractive clustering\cite{matlab}.
